MultiDataGrowthAssessPico

### 2023-12-07 Code/MultiDataGrowthAssessPico.Rmd
Editing MultiCultiGrowthAccessPico

---
title: "MultiDataGrowthAssess"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(tidyverse)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
#library(dplyr)
```

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn1 <- file.path("..","ProcessedData", "LogGrowthFits1")
DataIn2 <- file.path("..","ProcessedData", "LogGrowthFits2")
PlotsPath <- file.path("..","Plots")
ShinyPath <- file.path("..", "ShinyPico", "data")
DataOut <- file.path("..","GrowthAssessData")
MetaCatalog <- file.path("..","PicoCatalog.csv")

@@

GrowthTerm <- "Gompertz Growth Rate"

@@

```{r set colours}
MyWavelengths = c(405, 450, 475, 530, 615, 660, 730, "WW")
MCMIXColours = c("violet", "darkblue", "dodgerblue", "darkgreen","orange","red","purple", "black")

@@

```{r previous ProcessedData}
ProcessedFiles1 <- list.files(path = DataIn1, pattern = Project, full.names = TRUE)

ProcessedFiles1

ProcessedFiles2 <- list.files(path = DataIn2, pattern = Project, full.names = TRUE)

ProcessedFiles2
```

@@

## Read in ProcessedFiles .Rds 
## April 2023, Had to split the read in into 2 as there was not enough memory to read all files at once.

@@

LogFitsData1 <-  ProcessedFiles1 %>%
    map_df(~readRDS_plus(Flnm = .)) %>%
    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              "lognormOD720_Gompertz_param",
              "lognormdeltaOD_Gompertz_param",
              "OD720_logistic_param",
              "OD720trunc_exp_param",
              "deltaODtrunc_logistic_param",
              "OD720trunc_logistic_param",
              "deltaOD_logistic_param",
              "deltaODtrunc_exp_param"
              ))

LogFitsData2 <-  ProcessedFiles2 %>%
    map_df(~readRDS_plus(Flnm = .)) %>%
    select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              "lognormOD720_Gompertz_param",
              "lognormdeltaOD_Gompertz_param",
              "OD720_logistic_param",
              "OD720trunc_exp_param",
              "deltaODtrunc_logistic_param",
              "OD720trunc_logistic_param",
              "deltaOD_logistic_param",
              "deltaODtrunc_exp_param"
              ))

glimpse(LogFitsData1)
glimpse(LogFitsData2)

LogFitsData <- rbind(LogFitsData1, LogFitsData2)

remove(LogFitsData1)
remove(LogFitsData2)

>>>>

---
title: "MultiDataGrowthAssessPico"
author:
- Laurel Genge
- Carlie Barnhill
- Max Berthold
- Douglas A. Campbell
- Mireille Savoie
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(zoo)
library(RColorBrewer)
library(grid)
library(photobiologyWavebands)
#library(tidyquant)
#library(data.table)
#library(googledrive)
#library(googlesheets4)
#library(dplyr)
```

```{r set project variables}
#"..", takes up a level in the directory path

Project <- "PICO"

DataOut <- file.path("..", "Data", "CleanData", "CleanedMCData")
DataIn <- file.path("..", "Data","ProcessedData", "ProcessedMCData")

@@

@@

```{r set colours}

MyWavelengths = c(405, 445, 470, 530, 620, 660, 730, "WW")
MCMIXColours = c(c(w_length2rgb(405), w_length2rgb(445), w_length2rgb(470), w_length2rgb(530),
                   w_length2rgb(620), w_length2rgb(660), w_length2rgb(730), "black"))

@@

```{r previous ProcessedData}

ProcessedFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

ProcessedFiles

@@

## Read in ProcessedFiles .Rds

@@

LogFitsData <-  ProcessedFiles %>%
    map_df(~readRDS_plus(Flnm = .))

%>%
    # select(-c("Motivation", "doi", "SourceSalinity", "EndDate", "Salinity",  "InocpH","lognormdeltaOD_Gompertz", "lognormOD720_Gompertz", "OD720_logistic", "deltaOD_logistic","OD720trunc_logistic", "deltaODtrunc_logistic", "OD720trunc_exp", "deltaODtrunc_exp",
              # "lognormOD720_Gompertz_param",
              # "lognormdeltaOD_Gompertz_param",
              # "OD720_logistic_param",
              # "OD720trunc_exp_param",
              # "deltaODtrunc_logistic_param",
              # "OD720trunc_logistic_param",
              # "deltaOD_logistic_param",
              # "deltaODtrunc_exp_param"
              # ))
